What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
discussion finished v1

The exception (mis-)use patterns that emerged  in this study sheds enough light on 
problems that may be causeing the lack of rocustness of current Java programs in the face of
exceptional conditions: (i) the undocumented runtime exceptions thrown by library code - 
documenting runtime exceptions is a tedious and error prone task, to help developers
mitigating this problem tools should be developed to automate document runtime exceptions
scaping from library code. (ii) the odd wrappings found in this study can lead to what we call
an \emph{exception handling confusion problem} which may lead the problem to an
unpredictable state while trying to handle an exception. To illustrate this problem, we can use
 one of the examples found in this study: when the developer is 
confronted with a checked exception, the designer of the API is telling him 
to handle the exceptional condition, however we could observe that in some cases the 
checked exception wrapped an OutOfMemoryError, which represent resource deficiency detected 
by the JVM which make impossible the program to recover. Further investigation
is needed on finding ways to help developers in deadling with such problem, either preventing 
odd wrappings or enabling the developer to better dealing with them - when they are innevitable.

>>>>

The exception (mis-)use patterns that emerged  in this study sheds light on 
problems that may be causing the lack of robustness of current Java programs in the face of
exceptional conditions:
 \noindent\emph{The undocumented runtime exceptions} thrown by library code -
documenting runtime exceptions is a tedious and error prone task, to help developers
mitigating this problem tools should be developed to automate document runtime exceptions
scaping from library code, few solutions in this directions have been proposed so far ~\cite{van2005combining}. 
 \noindent\emph{The odd wrappings}  found in this study can lead to what we call
an \emph{exception handling confusion problem} which can lead the program to
an unpredictable state in the presence of exceptions. To illustrate this problem, we can use
 one of the examples found in this study: when the developer is 
confronted with a checked exception, the designer of the API is telling him 
to handle the exceptional condition, however we could observe that in some cases the 
checked exception wrapped an OutOfMemoryError, which represent resource deficiency detected 
by the JVM which make impossible the program to recover. Further investigation is needed on finding 
ways to help developers in deadling with such problem, either preventing odd wrappings or enabling 
the developer to better dealing with them.
